% ═════════════════════════════════════════════════════════════════════════════
% ACKNOWLEDGMENTS
% ═════════════════════════════════════════════════════════════════════════════

\mychapter{0}{Acknowledgments}

My greatest thank is to \textbf{Mr. Hamza Khalfi}, for his good guidance, the availability and the good advices. Many thanks to his valued comments and its profit which helped me organize and advance in my project.

It is with pleasure that I give my warm thanks to \textbf{Mrs. Nidal Lamghari}, Head of the Study Program, very warmly for its pedagogic coordination and good organizing of curriculum.

On the other side, I would have to thank \textbf{Mr. Abdelghani GHAZDALI}, Head of the Department, who has spontaneously assumed a responsibility for quality teaching and tried to set a welcoming atmosphere.

Last of all I would like to thanks all members of the academic and administration who provides a high level of education during my study.



I would like to thank very much my industrial tutor \textbf{Mr. Sebastien TRUPCEVIC} for the support and availability he had, more in general, for the knowledge sharing during the internship, as well as for the solutions that he always had for problems.



Secondly I would like to thank \textbf{Mr. Taha El Hafidi}, for his great help, support and contribution to this project.



I would like to thank all my colleagues and the team members, in particular \textbf{Mr. William Andre}, \textbf{Mr. Rachid Abdelmoumni}, \textbf{Mrs. Wiam El Arabi} and \textbf{Mr. Joan Andre}, as well as to the engineers collaborating with me, for their support, and collaboration, and friendly work environment.



Their encouragement, help and support and the will to pass on the benefits of their own experience turned this internship into a project that was both satisfying and extremely rewarding.

I want to express my gratitude to the jury for granting me the honor to examine and to evaluate this study.

 Last of all I would like to thank every one,  that helped me in some way, to make my experience in this project possible.


\clearpage