% ═════════════════════════════════════════════════════════════════════════════
% ABSTRACT
% ═════════════════════════════════════════════════════════════════════════════
\mychapter{0}{Abstract}

In a complex and industrial environment as the one described by STELLANTIS case, the governance information management (risks, responsibilities, deliverables status, gates progress) is made by distributed data located in multiple systems (SP, Excel files, etc..). As a consequence access problems were observed, information was inconsistent and a lot of time and effort was wasted by users answering to consolidated questions (‘Find responsible person for something’, ‘Verify status of something’, etc.).
\medskip

The purpose of this capstone is to develop and engineer a conversational agent LEON to be a helpful tool to engineering teams during governance operations. In this system, users interact with data via natural language for fast lookup of responsible parties and gate status or actions such as refresh or notify.
\medskip

The design of LEON is structured by a module approach comprising a combined conversational interface, workflow orchestration layer, a Specification validator and a data managing layer. The system is therefore easily understandable and adds flexibility to the overall architecture.
\medskip

Particular attention is given to the validation of specification by a deterministic process which uses rules so that the results are consistent and reproducible. We integrated also processes to achieve tracing of the operations and to follow the respect of the industrial rules.
\medskip
LEON accelerates the access to core governance data and enhance the consistency of processes. Additionally, the solution can be fully integrated into the existing infrastructures with minimal business disruption.
\vspace{1cm}


\noindent\rule[2pt]{\textwidth}{0.5pt}

{\textbf{Mots clés :}}
Technical governance, Conversation agent, Artificial intelligence, Specifications validation, Traceability, Automotive industry.\\
\noindent\rule[2pt]{\textwidth}{0.5pt}
